Supporting Information

### 2021-09-02 vertical-thermal-review.Rmd
add word count table (required by NewPhyt)

>>>>

Text | word count | other | n
---|---|-----|--------------------
Total word count (excluding summary, references and legends) | 	## |	No. of figures | 	4 (all colour)
Summary|  	183 | 	No. of Tables | 	2  
Introduction|	## |	No of Supporting Information files | 	##
Review of vertical gradients |	##	||	 
Implications |	##	 ||
Conclusions |	##	||
Acknowledgments | ##	||
